---
title: "INCENTIVE BARCELONA 45 PAX"
author: "BUSINESS TRAVEL CORPORATE"
date: 'September 25th to 27th 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(shiny)
library(dplyr)
library(knitr)
library(timevis)

```

## Accommodation

### **HOTEL BARCELO RAVAL**


```{r child='BarceloRaval.Rmd'}

```

  <br>
  
    Rates in Barcelo Raval per room per night:
    Double room for single use buffet breakfast included €210
    Double room for double use buffet breakfast included €230
    City tax (per preson per day) €1,21
    Option dated July 8th
  <br>
  

### Alternative Hotels {.tabset .tabset-fade .tabset-pills}

#### **HOTEL CATALONIA PUTXET**


```{r child='CataloniaPutxet.Rmd'}

```

  <br> 
  
    Rates in Catalonia Putxet per room per night:
    Double room for single use buffet breakfast included €150
    Double room for double use buffet breakfast included €170
    City tax (per preson per day) €1,21
    Option dated shared with other agency, which has requested the same group
  <br>
  
  

*****

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business Travel Corporate
  
  * For a group of minimum 45 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
*****





